\documentclass[margin,line]{res}
\usepackage{mathpazo, verbatim, hyperref}

%\setlength{\paperwidth}{8.5in}
%\setlength{\paperheight}{11in}

\topmargin=-0.3in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.2in
\textheight=9.5in
%\itemsep=0in
%\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{8.5in}%\paperwidth}
\setlength{\pdfpageheight}{11in}%\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}
\moveleft.5\hoffset\centerline{\large\bf Andy C. Huang}
%\moveleft\hoffset\vbox{\hrule width 7.5in height 1pt}\smallskip
\moveleft.5\hoffset\centerline{{\it e-mail:}  andy.c.huang@outlook.com}
%\moveleft.5\hoffset\centerline{{\it webpage:} \url{http://math.rice.edu/~ach3}}
\moveleft.5\hoffset\centerline{{\it GitHub:} \url{https://github.com/andy-c-huang}}
\moveleft.5\hoffset\centerline{{\it cellphone:}  (408) 887 - 9651}
\vspace*{.1in}

\begin{resume}

%\section{\sc Objective} I am seeking a position in research and development allowing me to use the rigorous analytical skills I've developed from my doctoral training in mathematics. I thrive in an environment requiring collaboration with engineers from other areas,

\vspace*{-6pt}

\section{\sc Education and Honors}
{\bf Rice University}, Houston, TX \hfill
%\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. in Mathematics (Advisor: Dr. Mike Wolf, GPA 3.96) \hfill May 2016
\item[] \hskip .2in {\em Dissertation Title:} "Handle crushing harmonic maps between surfaces"
\vskip -6pt
\item[] M.A. in Mathematics (GPA: 4.04) \hfill May 2012
\end{list1}
\vskip -12pt
{\bf University of California, Davis}, Davis, CA
\begin{list1}
\item[] B.S. in Mathematics with Departmental Citation (Major GPA: 3.85) \hfill May 2010
\end{list1}
\vskip -12pt
{\bf Budapest Semesters in Mathematics}, Budapest, Hungary \hfill Dec 2009

\section{\sc Computer skills}
{\em Programming languages:} C++, C, Python \\
{\em Software:} Trilinos, Git, MATLAB, Mathematica, CUBIT, ParaView, \LaTeX, OpenCV, scikit-learn

\section{\sc Professional Experience}
{\bf Sandia National Laboratories}, Albuquerque, NM \hfill {\bf Jan 2019 - present}\\
{\em Senior Member of the Technical Staff, Computer Science}\\
Code developer for two MPI-parallel and GPU supported C++ physics simulation codes, for semiconductor physics and electromagnetcs. Main work and research focus on numerical formulations, solver acceleration and stability, and physics implementation. On-going work include:
\begin{itemize}
\setlength\itemsep{0pt}
\item[-] Acceleration of frequency-domain analysis in semiconductor physics simulation code, \newline Charon (project homepage: \url{https://charon.sandia.gov}).
\item[-] Multi-physics coupling of some of Sandia's simulation codes, including Xyce.
\item[-] Electromagnetics simulation code solver acceleration for high-performance computing platforms.
\end{itemize}

{\bf Sandia National Laboratories}, Albuquerque, NM \hfill {\bf Jul 2016 - Jan 2019}\\
{\em Postdoctoral appointment (within Sandia's semiconductor device modelling team)}\\
Designed and implemented (in C++) a frequency-domain analysis method in Sandia's semiconductor device physics simulation code, Charon. Required extensive communication and cooperation with other developers to minimize disruption while extending code capability.

{\bf Sandia National Laboratories}, Albuquerque, NM \hfill {\bf May 2015 - Jun 2016}\\
{\em Graduate student intern, mentor: Xujiao (Suzey) Gao}\\
Compared and analyzed numerical stabilization schemes for finite element and control volume methods for the simulation of coupled transient drift-diffusion equations modelling semiconductor physics. Implemented these stabilization schemes in Sandia's TCAD program, Charon (in C++).

\section{\sc Research and Projects}

{\bf Modeling of harmonic maps between surfaces \hfill Mar 2012 - Jun 2016}\\
Implementation of finite element methods in Matlab, and porting to Python with C libraries for optimization. Analyzed a transient semi-linear elliptic PDE. Obtained for examples considered in thesis.
\vskip -5pt
{\bf Developed a Windows 8.1 phone app: ``KnowYoNotes" \hfill Feb 01, 2015}\\
\emph{GitHub repo avilable at: }\url{https://github.com/andy-c-huang/KnowYoNotes}\\
Developed the interface for a sheet music reading learning app. Written in C\#, involving event driven programming. Further development ongoing. Created for Rice's 2015 24 hour hackathon, HackRice.
\vskip -5pt
{\bf Travelling wave phenomena: Wave reflection in excitable media \hfill Sept 2008 - Jun 2009} \newline
%{\em (in collaboration w/ Prof. Timothy Lewis (UC Davis), funded by the McNair Scholars program and the NSF)} \newline
Investigated wave reflection phenomena in modified, coupled Fitzhugh-Nagumo equations. Explored existence and stability of anti-phase behavior in periodic solutions - interpreted biologically as a cause for cardiac arrhythmia. McNair Scholars Program funded. Advisor: Dr. Timothy Lewis (UC Davis).
\vskip -5pt
{\bf Spread of Avian Influenza Across Heterogeneous Farmscapes \hfill Sept 2007 - Sept 2008} \\
%{\em (as an undergraduate cohort member of the 2007, UC Davis and NSF funded interdisciplinary Collaborative Learning at the Interface of Math and Biology group)} \\
Modeled spread of the H5N1 virus on farm networks of varying spatial heterogeneity using coupled, stochastic compartment models. Analyzed effect of heterogeneity on potential for a large outbreak. Presented to panel of poultry industry leaders, including Foster's Farms. UC Davis and NSF funded.

\section{\sc Grants and Awards}
\begin{enumerate}
  
\item SIAM Science Policy Fellowship \hfill {\bf Jan 2019 - Dec 2020}
\item GEAR Graduate Internship award \hfill {\bf Mar 2016} \\
to work with Dr. Domingo Toledo at the University of Utah in Salt Lake City, Utah
\item GEAR short-term visit award \hfill {\bf Jun 2015} \\
to work with Dr. Bill Goldman at the Mathematical Sciences Research Institute in Berkeley, CA
\item National Association of Math Circles Exchange grant \hfill {\bf 2014}
\item National Association of Math Circles Seed grant \hfill {\bf 2013}
\end{enumerate}

\section{\sc Publications and Presentations}
\begin{enumerate}
\item \emph{An Isofrequency Remapping Scheme for Harmonic Balance Methods} \hfill{\bf Feb. 26, 2019}\\
      SIAM Conf. on Computational Science and Engineering in Spokane, WA
\item \emph{Analytic band-to-trap tunneling model including band offset for heterojunction devices}\\
      Xujiao Gao, Bert Kerr, and Andy Huang\\
      In: Journal of Applied Physics 125, 054503 (2019)\\
      \url{https://doi.org/10.1063/1.5078685}
\item \emph{Non-degenerate harmonic balance via isofrequency remapping}\\
      (in preparation)
\item \emph{Developing a harmonic balance method for Charon}  \hfill {\bf Oct. 24, 2018}\\
      Trilinos Users Group meeting in Albuquerque, NM
\item \emph{A versatile harmonic balance method in a parallel framework} \hfill {\bf Sept 25, 2018}\\
      A. Huang, X. Gao, R. Pawlowski, J. Gates, L. Musson, G. Hennigan, M. Negoita\\
      International Conference on Simulation of Semiconductor Processing and Devices (SISPAD)\\
      \url{http://dx.doi.org/10.1109/SISPAD.2018.8551620}
\item \emph{A harmonic balance method for PDEs} (SAND2016-12293)
\item \emph{Development of harmonic balance capability for Charon} (SAND2018-3623)
\item {\em Efficient band-to-trap tunneling model including heterojuntion band offset}\\
      Xujiao Gao, Andy Huang, and Bert Kerr\\
      In: ECS Transactions, vol. 80, pp. 1005–1015, 2017.
\item {\em Harmonic maps of punctured surfaces to the hyperbolic plane} \\%\hfill {\bf May 25, 2016} \\
      In: {\em Communications in Analysis and Geometry} (to appear) \\
      Preprint available at \url{http://arxiv.org/abs/1605.07715}
\item {\em Using geometric maximum principles to harmonically crush handles} \hfill {\bf Sep 10, 2016} \\
      GEAR Workshop: Analytic Aspects of Higher Teichm\"uller Theory at Rutgers University, Newark
\item {\em Handle crushing harmonic maps between surfaces} \hfill {\bf Mar 30, 2016} \\
      Max Dehn Seminar at the University of Utah, Math Department
\item {\em On harmonic maps between non-compact surfaces of different genera} \hfill {\bf Nov 15, 2015} \\
      AMS Special Session (at Rutgers Univ.): Aspects of Minimal Surfaces in Riemannian Manifolds
\item {\em Implementation of different stabilization schemes in Charon using Trilinos/Panzer} \hfill{ \bf Oct. 27, 2015} \\
      X. Gao, A. Huang, K. Peterson, G. Hennigan, L. Musson, and P. Bochev \\
      Presented by X. Gao at the Trilinos User Group meeting Albuquerque, NM
\end{enumerate}

\section{\sc Professional development}
Enthought's Machine Learning Mastery Workshop (May 21-23 2018)\\
Kokkos tutorial (Dec. 5, 2017)\\
Enthought's Python for Scientists and Engineers (Sept. 11-15, 2017)\\
Introduction to CUBIT (Nov. 15, 2016)\\
ParaView (Aug. 3-5, 2016)

\section{\sc Conferences}
Trilinos User-Developer Group meeting in Albuquerque, NM (Oct 23-25, 2018)\\
Intl. Conf. on Simulation of Semiconductor Processing and Devices in Austin, TX (Sept. 24-26, 2018)\\
IEEE Intl. Symp. on Antennas and Propagation APS/USRI in Boston, MA (Jul 8-13, 2018)\\
Trilinos User-Developer Group meeting in Albuquerque, NM (Oct. 23-25, 2017)\\
SIAM Conference on Computational Science and Engineering in Atlanta, GA (Feb 27 - Mar 3, 2017)

\section{\sc Leadership}
{\bf Head Mechanic at Rice Bikes \hfill Jul 2013 - May 2016} \\
Oversaw student-run bike shop mechanic training at Rice University. Organized bike builds for the rental bike fleet, using it as a training platform for team of 10. Coordinated monthly, themed bike rides for Rice students to safely tour areas of Houston. Re-structured mechanics operations for efficiency.
\vskip -5pt
{\bf Rice Math Circle co-organizer \hfill Aug 2012 - May 2014}\\
%Graduate student operated math circle for middle- and high-school aged students.
Coordinated and designed 3-hour, bi-weekly sessions run by graduate students exploring math topics through problems, puzzles, and games. Middle- and high-school student audience. Topics included: graph theory, discrete probability, combinatorics, game theory, minimal surfaces, programming.
\vskip -5pt
{\bf Instructor (at Rice University)} \\
Ordinary Differential Equations (Math 211), Calculus II (Math 102) \hfill {\bf Spring 2013, Summer 2012}
\vskip -5pt
{\bf Teaching Assistant \hfill Sept 2010 - May 2016}\\
Conducted office hours, led weekly discussions, and graded homework. {\em Courses:} Single and multi-variable calculus, Ordinary and partial differential equations, Riemannian geometry, Real Analysis

\section{\sc Service and Outreach}
{\bf Math Counts volunteer \hfill Feb 10, 2018}\\
scored exams from Math COUNTS competition at Albuquerque Academy
\vskip -5pt
{\bf Community Involvement brainstorm \hfill Dec 12, 2016}\\
Participated in a discussion lead by Tineca Quintana (org 3652)
\vskip -5pt
{\bf ``Changing the Equation" Career Spotlight interview \hfill Dec 6, 2016}\\
used in Explora math kits designed for after school activities, put together by Amy Tapia (org 3652)
\vskip -5pt
{\bf Mars Bus Experience volunteer \hfill Oct 27, 2016}\\
at Van Buren Middle School, organized by Tineca Quintana (org 3652)
\vskip -5pt
{\bf Invited presenter: ``How to be efficient (in some sense)" \hfill Mar 14, 2015} \\
as part of a Pi Day celebration at NASA's Space Center Houston
\vskip -5pt
{\bf Minimal surfaces and soap films demonstration \hfill Nov 4, 2012} \\
as part of the Weiss School of Natural Sciences alumni open house at Rice University

\begin{comment}
\section{\sc Hobbies and Interests}
Bicycling, rock climbing, racquetball, Arduino hacks
\end{comment}


\end{resume}
\end{document}




